---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `unitBSQuantReg`: unit-Birnbaum-Saunders quantile regression

<!-- badges: start -->
<!-- badges: end -->

The goal of unitBSQuantReg is to provide tools for fitting unit-Birnbaum-Saunders
quantile regression proposed by Mazucheli et al. (2021)

## Installation


You can install the development version of `unitBSQuantReg` from [GitHub](https://github.com/AndrMenezes/unitBSQuantReg) with:

``` r
# install.packages("remotes")
remotes::install_github("AndrMenezes/unitBSQuantReg")
```

## Example

The packages follows the structure of `glm` object. The main function is `unitBSQuantReg`.

```{r example}
library(unitBSQuantReg)
u <- "http://www.leg.ufpr.br/lib/exe/fetch.php/publications:papercompanions:qbmult_dataset.csv"
bodyfat <- read.table(u, sep = ",", header = TRUE)

bodyfat$BMI <- bodyfat$BMI / 100
bodyfat$SEX <- factor(bodyfat$SEX)
bodyfat$IPAQ <- factor(bodyfat$IPAQ)
bodyfat$ARMS <- bodyfat$ARMS / 100
taus <- c(0.10, 0.25, 0.50, 0.75, 0.90)
fits <- lapply(taus, function(t) {
 unitBSQuantReg(ARMS ~ BMI + AGE + SEX + IPAQ, data = bodyfat, tau = t) 
})
names(fits) <- paste0("tau = ", taus)

sapply(fits, coef)
```

The currently methods implemented are

```{r}
methods(class = "unitBSQuantReg")
```


- Mazucheli, J., Leiva, V., Alves, B., Menezes, A. F. B. (2021) A New Quantile Regression for Modeling Bounded Data Under a Unit Birnbaum-Saunders Distribution with Applications in Medicine and Politics. [_Symmetry_](https://www.mdpi.com/journal/symmetry), to appear.


